The Linguistic Landscape of Stream-of-Consciousness Literature

### 2024-04-03 paper/paper.qmd
update paper

By analyzing these textual datasets, I seek to pose and answer crucial questions: What are some important factors contributing to this relationship between mental health, disassociation and stream of consciousness? Moreover, how does this relationship vary differently across differnet demographics of authors, for instance, authors with different geographical locations and genders? Understanding these dynamics is crucial in having an informed understanding of the West's late 19th to mid-20th century socio-political landscape, especially in regards to how authors and creative writers navigate and deal with then-taboo topics such as existential angst, mental health issues and disabilities.

>>>>

By analyzing these textual datasets, I seek to pose and answer crucial questions: \textit{What are some important factors contributing to this relationship between mental health, disassociation and stream of consciousness? Moreover, how does this relationship vary differently across differnet demographics of authors, for instance, authors with different geographical locations and genders?} Understanding these dynamics is crucial in having an informed understanding of the West's late 19th to mid-20th century socio-political landscape, especially in regards to how authors and creative writers navigate and deal with then-taboo topics such as existential angst, mental health issues and disabilities.
